### 2015-10-28 dynamo/dynamo.tex
Aggiunto il main (main.tex); Modificato il nome di /COPS/slide.tex in /COPS/cops.tex; Aggiunto il file /dynamo/dynamo.tex; Tolto l'attributo "handout" in \documentclass.

\section{Dynamo}
\begin{frame}
  \frametitle{Dynamo}

\end{frame}